No Title

### 2017-10-26 paper/paper.tex
abstract

\begin{abstract}
We quantify the joint spatial distribution of satellites around the Milky way and Andromeda.
\end{abstract}

@@

In Section we list the sources of the observatinal and
simulated data to be used throughout the paper.
Next, in Section we describe the methods we use to quantify and
characterize the satellite distributions.
In section we present our results. 
First we describe the observed satellite distributions and compare
them against the expectation of an spherical randomization of its
satellites. We then compute the expectation from the Illustris Simulation. 
In Section we discuss the implication of our results to finally
summarize in Section.

@@

The smallest satellites are barely resolved in stellar mass at magnitudes of
$M_V=9$, however its dark matter structure is sampled with at least
$100$ particles. 
We find that all considered halos have at least $XX$ subhalos above
a maximum circular velocity of $15$\kms.
For this reason we select the satellite galaxy samples from the
DM subhalo population and not from the galaxies with photometry.
We chose in two different ways the sub-halo samples. 
First, we rank the halos by decreasing order of its maximum circular
velocity and select the first $N_p$ halos in the list.
Second, we select all satellites above maximum circular velocity of
$20$\kms to randmbly subsample $N_p$ subhalos.

We build a sample of Local Group Analgues (LGA) by selecting first all
galaxies with  an stellar mass in the range $1\times10^{10}\Msun
<M_{\star}<1.5 \times 10^{11} \Msun$.
Then we consider the following criteria for all galaxies in that
sample.

\begin{itemize}
\item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two are considered as a pair. 
\item With $d_{AB}$ the distance between the two galaxies and
  $M_{\star,min}$ the lowest stellar mass in the two galaxies, we
  discard pairs that have any other galaxy $C$ with stellar mas
  $M_{\star}>M_{\star, min}$ closer than $3\times d_{AB}$ from any of
  the pair's members. 
\item The distance $d_{AB}$ greater than $700$ kpc.
\item The relative radial velocity between the two galaxies, including
  the Hubble flow, is $-120\ \kms <v_{AB,r}<0\ \kms$. 
\end{itemize}

We find 27 pairs with these conditions. Figure shows the physical 
properties (stellar masses, maximum circular velocities, radial
velocities and separation) in those pairs.

@@

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{correlations_M31.pdf}
\includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
\caption{Correlations between the normalized values for the plane
  width, $c/a$ ratio and $b/a$ ratio. 
The star corresponds to the LG, black circles with errorbars are the
results from simulations and the gray cloud is the resul from the
multivariate gaussian model.
Upper raw summarizes the results for M31 and the lower raw for the MW.
This simplified description allows us to quantify how atypical is the
LG compared to the simulation results. 
\label{fig:correlations}}
\end{figure*}

@@

>>>>

\begin{abstract}
We quantify the joint spatial distribution of the brightest satellites
around the Milky way and M31. 
We find that the satellites in MW show a distribution significantly
thinner and flattened compared to the expectaions of a random
spherical distribution and simulations based on the Lambda Cold Dark
Matter paradigm.
In turn, M31 is completely consistent with the expectations from a
spherical satellite distribution and LCDM simulations.
The satellite planes in the MW and M31 are almost perpendicular to the line
connecting the two galaxies. None of the pairs in the simulation show
a similar degree of alignment. 
However, the simulations are consistent with a random uniform
distribution, making the result from the observations consistent with
these theoretical expectations.
This special satellite distribution in the Milky Way makes the Local
Group an atypical pair in the expected cosmological context.
We summarize these results in a simple multivariate Gaussian
model to estimate that only $1\%$ of the pairs with isolation
and dynamical characteristics similar to the LG are expected to have
satellite distributions with the same degree of atipicality. 
\end{abstract}

@@

In Section we list the sources of the observational and
simulated data to be used throughout the paper.
Next, in Section we describe the methods we use to quantify and
characterize the satellite distributions.
In section we present our results. 
In the discussion section we quantify the correlations between the main
plane properties as described by the simulations.
We use this results to quantify the degree of atipicality of the LG
and estimate the volume that has to probed in simulations in order to
find a pair with a satellite distribution as atipical as the LG. 
Finally, we summarize our conclusions in Section .

@@

We buid a sample of Isolated Pairs that resemble the conditions
in the LG.
To construct this sample we select first all galaxies with  an stellar mass in the range $1\times10^{10}\Msun
<M_{\star}<1.5 \times 10^{11} \Msun$.
Then we consider the following criteria for all galaxies in that set.

\begin{itemize}
\item For each galaxy $A$ we find its closest galaxy $B$, if galaxy $A$ is also
the closest to halo $B$, the two are considered as a pair. 
\item With $d_{AB}$ the distance between the two galaxies and
  $M_{\star,min}$ the lowest stellar mass in the two galaxies, we
  discard pairs that have any other galaxy $C$ with stellar mass
  $M_{\star}>M_{\star, min}$ closer than $3\times d_{AB}$ from any of
  the pair's members. 
\item The distance $d_{AB}$ is greater than $700$ kpc.
\item The relative radial velocity between the two galaxies, including
  the Hubble flow, is $-120\ \kms <v_{AB,r}<0\ \kms$. 
\end{itemize}

We find 27 pairs with these conditions. We show in the Appendix A the
physical  properties (stellar masses, maximum circular velocities,
radial velocities and separation) in those pairs. 
We then select the pairs where in both halos there are at least 15
detected subhalos. 
We end up with a total of 20 pairs that fulfill these criteria.

Although Illustris-1 has stellar particles, we do not use their
properties to select the satelite population because the smallest
galaxies are barely resolved in stellar mass at magnitudes of
$M_V=9$. We prefer using the dark matter information as the smallest
sub-halos are sampled with $100$ particles. 
For this reason we select the satellite galaxy samples from the

We chose the satellite samples by ranking the subhalos in decreasing
order of its maximum circular velocity and select the first $N_p$
halos in the list. 
The results in the main body of the paper correspond to $11\leq
N_p\leq 15$.

@@

\begin{figure*}
\centering
\includegraphics[width=1.0\textwidth]{correlations_M31.pdf}
\includegraphics[width=1.0\textwidth]{correlations_MW.pdf}
\caption{Correlations between the normalized values for the plane
  width, $c/a$ ratio and $b/a$ ratio. 
The star corresponds to the LG, black circles with errorbars are the
results from simulations and the gray cloud is the resul from the
multivariate gaussian model.
Upper/lower row summarizes the results for M31/M31.
This simplified description allows us to quantify how atypical is the
LG compared to the simulation results. 
\label{fig:correlations}}
\end{figure*}

@@

Prospects for observational measurement: DESI.
